\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-23 europa-basics.tex
Made sure that paragraph tittles are correctly displayed in italic

\paragraph \textit{Constraint Satisfaction}: A canonical problem in
dealing with constraints is the $N$-Queens problem in which chess queens
must be placed on an  $N$x$N$ chessboard so no queens attack the other. % Fig.
% \ref{fig:nqueens-1} shows an example of a random positioning of queens
% on a  $N$x$N$ chessboard. Queens in violation of the non-attack constraint
% are highlighted in red.
% \begin{figure} \centering
%   \includegraphics[scale=0.35]{figs/Example-NQueens0.jpg}
%   \caption{\small N-Queens problem. Queens in violation of the
%     non-attack constraint are highlighted in red.}
% \label{fig:nqueens-1}
% \vskip+0.1cm
% \end{figure}
If we define $N$x$N$ variables Q$_{rc}$, $r \in [1,N]$, $c \in [1,N]$,
Q$_{rc} = 1$ if cell $r,c$ in the chessboard is occupied by a Queen,
$0$ otherwise. Then the following constraints need to be satisfied:

@@

\paragraph \textit{Scheduling}: In the Resource Constrained Project
Scheduling Problem (\texttt{RCPSP}) \cite{Bruckera99}, a project
consisting of a set of activities must be scheduled in a way that
satisfies minimum and/or maximum temporal separation constraints. The
activity schedule must also respect fixed limits on the availability
of resources required to perform each activity. In addition to
satisfying temporal and resource constraints, it is common for the
user to want to minimize makespan \cite{ghallab04} so that the entire
project is finished as early as possible. Fig. \ref{fig:rcpsp-1} shows
an example of a a solution provided by \eu for an \texttt{RCPSP}
instance with 10 activities, 5 resources and 30 temporal constraints.

@@

\paragraph \textit{Planning}: In the Shopping Agent Problem
\cite{russelnorvig} an agent needs to purchase a set of products
(milk, drill, etc) that are available at specific locations
(supermarket, hardware store, etc) and the agent is subject to
temporal (must complete tasks by specific deadlines) and resource
(fuel, carrying capacity, etc) constraints. The agent needs to figure
out what actions need to be performed to find and acquire the required
items, as well as when to perform each of those
actions. Fig. \ref{fig:shopping-1} shows a solution produced by \eu
for such a problem instance.

@@

\item If the structure of a planning model (actions, conditions,
  effects, dependencies at the action level) is not explicitly
  maintained by the CSP planner, the search algorithms are deprived of
  critical information to make better decisions. If that structure is
  maintained (for instance, by internally marking variables that
  represent action choice and relationships between actions), it is
  still hard to write search algorithms as any planning-specific
  insight has to be translated into the CSP representation of
  variables and constraints.

@@

These drawbacks have been addressed by a number of planning frameworks
like \texttt{Descartes} \cite{joslin95,joslin96}, \texttt{IxTet}
\cite{ghallab87,lemai04} and \texttt{CAIP} (Constraint-Based Interval
and Attribute Planning) \cite{mus94,frank2003}.  These frameworks take
advantage of a CSP representation to deal with time and resources, at
the same time maintaining an explicit representation of the elements
relevant to planning (action choices, causal relationships, etc). This
combination results in a planning approach that can deal with the type
of constraints found in real-world problems while allowing for
intuitive problem descriptions and a natural way to express search
algorithms and heuristics. \eu is one such implementation of the
\texttt{CAIP} framework, in which planning problems are specified in
terms of:

>>>>

\paragraph{} {\em Constraint Satisfaction}: A canonical problem in
dealing with constraints is the $N$-Queens problem in which chess queens
must be placed on an  $N$x$N$ chessboard so no queens attack the other. % Fig.
% \ref{fig:nqueens-1} shows an example of a random positioning of queens
% on a  $N$x$N$ chessboard. Queens in violation of the non-attack constraint
% are highlighted in red.
% \begin{figure} \centering
%   \includegraphics[scale=0.35]{figs/Example-NQueens0.jpg}
%   \caption{\small N-Queens problem. Queens in violation of the
%     non-attack constraint are highlighted in red.}
% \label{fig:nqueens-1}
% \vskip+0.1cm
% \end{figure}
If we define $N$x$N$ variables Q$_{rc}$, $r \in [1,N]$, $c \in [1,N]$,
Q$_{rc} = 1$ if cell $r,c$ in the chessboard is occupied by a Queen,
$0$ otherwise. Then the following constraints need to be satisfied:

@@

\paragraph{} \textit{Scheduling}: In the Resource Constrained Project
Scheduling Problem (\texttt{RCPSP}) \cite{Bruckera99}, a project
consisting of a set of activities must be scheduled in a way that
satisfies minimum and/or maximum temporal separation constraints. The
activity schedule must also respect fixed limits on the availability
of resources required to perform each activity. In addition to
satisfying temporal and resource constraints, it is common for the
user to want to minimize makespan \cite{ghallab04} so that the entire
project is finished as early as possible. Fig. \ref{fig:rcpsp-1} shows
an example of a a solution provided by \eu for an \texttt{RCPSP}
instance with 10 activities, 5 resources and 30 temporal constraints.

@@

\paragraph{} \textit{Planning}: The Shopping Agent Problem
\cite{russelnorvig} is a variation of the problem with which we started this chapter.
In this problem, an agent needs to purchase a set of products
(milk, drill, etc) that are available at specific locations
(supermarket, hardware store, etc) and the agent is subject to
temporal (must complete tasks by specific deadlines) and resource
(fuel, carrying capacity, etc) constraints. The agent needs to figure
out what actions need to be performed to find and acquire the required
items, as well as when to perform each of those
actions. Fig. \ref{fig:shopping-1} shows a solution produced by \eu
for such a problem instance.

@@

\item If the structure of a planning model (actions, conditions,
  effects, dependencies at the action level) is not explicitly
  maintained by the \textsf{CP} planner, the search algorithms are deprived of
  critical information to make better decisions. If that structure is
  maintained (for instance, by internally marking variables that
  represent action choice and relationships between actions), it is
  still hard to write search algorithms as any planning-specific
  insight has to be translated into the \textsf{CP} representation of
  variables and constraints.

@@

These drawbacks have been addressed by a number of planning frameworks
like \texttt{Descartes} \cite{joslin95,joslin96}, \texttt{IxTet}
\cite{ghallab87,lemai04} and \texttt{CAIP} (Constraint-Based Interval
and Attribute Planning) \cite{mus94,frank2003}.  These frameworks take
advantage of a \textsf{CP} representation to deal with time and resources, at
the same time maintaining an explicit representation of the elements
relevant to planning (action choices, causal relationships, etc). This
combination results in a planning approach that can deal with the type
of constraints found in real-world problems while allowing for
intuitive problem descriptions and a natural way to express search
algorithms and heuristics. \eu is one such implementation of the
\texttt{CAIP} framework, in which planning problems are specified in
terms of:
